Supplementary Materials: Introductory Physics Labs: A Tale of Two Transformations

### 2020-10-07 supplement/supplement.tex
Edits to supplement.

Regional State University is a public doctoral granting university in a rural, economically
depressed part of our state.  The university mission is focused on regional transformation and
service to this region.  The total combined student population in Fall 2019 was 28,651 largely
comprised of undergraduates (23,081).Our physics labs (Physics 1 lab and Physics 2 lab) are
each 1 credit courses that meet for 2 hours per week. These courses serve both of our
Calculus-based and Algebra-based physics lecture courses.  Most $(\sim 75\%)$ of the students
who take our lab course are in (or have taken) the Algebra-based physics lecture course. It
also fulfills the general education requirement for science lab courses at our university.
Table \ref{tab:gender} compares the gender of students in these lab courses compared to the
university population.  We note that the gender distribution of students in the Physics 2 lab
generally matches the university population, while the Physics 1 lab skews more heavily male
than the university population.  We also compare the race of students in these contexts in
Table \ref{tab:race}.  The racial and ethnic profile of students in our lab courses is similar
to the university.

@@

Labs are supervised by Author 2, but each section is run by Graduate GTAs (GTAs). The
transformed curriculum was jointly written by both of the authors.  GTA training was greatly
enhanced when the new lab curriculum was put in place.  Both authors, along with colleagues in
Biology and Chemistry, run a training for all GTAs in Biology, Chemistry, Geology, and Physics
as these disciplines are all using the same curricular format for their labs.  Author 2 runs a
weekly prep meeting with the GTAs, and SFW and the research team have supervised various
aspects of the transformation especially important for research such as curricular
implementation \citep{SmithJoyner2020} and assessment grading practices \citep{Wolf2019}.

@@

\begin{table}
  \caption{\label{tab: 1251 fall} General Physics Laboratory I investigations for Fall 2020
    block schedule.}
  \begin{tabular}{ccp{28em}}
    \hline\hline
    Investigation & Topic & Guiding Question\\
    \hline
    1 & 1-D kinematics & Does a ball rolling on an incline have the same acceleration on the way up as it does on the way down? \\
    2 & Periodic motion & At what nut position is the period of the physical pendulum equal to \SI{1.30}{s}? \\
    3 & 2-D collisions & Is the collision between two marbles elastic? \\
    \hline\hline
  \end{tabular}
\end{table}

@@

\begin{table}
  \caption{\label{tab: 1251 lab kit} General Physics Laboratory I lab kit contents.}
  \begin{tabular}{clc}
    \hline\hline
    Quantity & Item & Investigation(s)\\
    \hline
    1 & Protractor & 1 \\
    2 & \SI{25}{mm} marble & 1, 3 \\
    1 & Tape measure with cm scale & 1, 2, 3\\
    1 & \SI{0.6}{m} threded rod & 2 \\
    1 & Eye nut & 2 \\
    3 & Nuts & 2 \\
    1 & Door hook & 2 \\
    1 & \SI{1}{m} string & 2 \\
    1 & \SI{16}{mm} marble & 3 \\
    \hline\hline
  \end{tabular}
\end{table}

We developed lab kits with supplies that allowed the students to perform the investigations
outside the teaching laboratory. We purchased the lab kit items in collaboration with our
campus bookstore, and the students purchased the lab kits from the bookstore. We ordered lab
kit items in bulk and where possible directly from manufacturers to reduce the costs of the
items. Each General Physics Laboratory I kit costs \textcolor{red}{$\sim$}\$25.00, and each
General Physics Laboratory II kit costs \$39.00. Table \ref{tab: 1251 lab kit} shows the lab
kit contents for General Physics Laboratory I, and Table \ref{tab: 1261 lab kit} shows the lab
kit contents for General Physics Laboratory II.

>>>>

Regional State University is a public doctoral granting university in a rural, economically
depressed part of our state.  The university mission is focused on regional transformation and
service to this region.  The total combined student population in Fall 2019 was 28,651 largely
comprised of undergraduates (23,081).  Our physics labs (Physics 1 lab and Physics 2 lab) are
each 1 credit courses that meet for 2 hours per week. These courses serve both of our
Calculus-based and Algebra-based physics lecture courses.  Most $(\sim 75\%)$ of the students
who take our lab course are in (or have taken) the Algebra-based physics lecture course. It
also fulfills the general education requirement for science lab courses at our university.
Table \ref{tab:gender} compares the gender of students in these lab courses compared to the
university population.  We note that the gender distribution of students in the Physics 2 lab
generally matches the university population, while the Physics 1 lab skews more heavily male
than the university population.  We also compare the race of students in these contexts in
Table \ref{tab:race}.  The racial and ethnic profile of students in our lab courses is similar
to the university.

@@

Labs are supervised by Author 2, but each section is run by Graduate TAs (GTAs). The
transformed curriculum was jointly written by both of the authors.  GTA training was greatly
enhanced when the new lab curriculum was put in place.  Both authors, along with colleagues in
Biology and Chemistry, run a training for all GTAs in Biology, Chemistry, Geology, and Physics
as these disciplines are all using the same curricular format for their labs.  Author 2 runs a
weekly prep meeting with the GTAs, and Author 1 and the research team have supervised various
aspects of the transformation especially important for research such as curricular
implementation \citep{SmithJoyner2020} and assessment grading practices \citep{Wolf2019}.

@@

\begin{table}
  \caption{\label{tab: 1251 fall} General Physics Laboratory I investigations for Fall 2020
    block schedule.}
  \begin{tabular}{ccp{28em}}
    \hline\hline
    Investigation & Topic & Guiding Question\\
    \hline
    1 & 1-D kinematics & Does a ball rolling on an incline have the same acceleration on the way up as it does on the way down? \\
    2 & 2-D collisions & Is the collision between two marbles elastic? \\
    3 & Periodic motion & What is the nut position for which the physical pendulum small-angle period is minimum, and what is the power-law regression equation for the period of the system? \\
    \hline\hline
  \end{tabular}
\end{table}

@@

\begin{table}
  \caption{\label{tab: 1251 lab kit} General Physics Laboratory I lab kit contents.}
  \begin{tabular}{clc}
    \hline\hline
    Quantity & Item & Investigation(s)\\
    \hline
    1 & Protractor & 1 \\
    2 & \SI{25}{mm} marble & 1, 2 \\
    1 & Tape measure with cm scale & 1, 2, 3\\
    1 & \SI{0.6}{m} threded rod & 3 \\
    1 & Eye nut & 3 \\
    3 & Nuts & 3 \\
    1 & Door hook & 3 \\
    1 & \SI{1}{m} string & 3 \\
    1 & \SI{16}{mm} marble & 2 \\
    \hline\hline
  \end{tabular}
\end{table}

We developed lab kits with supplies that allowed the students to perform the investigations
outside the teaching laboratory. We purchased the lab kit items in collaboration with our
campus bookstore, and the students purchased the lab kits from the bookstore. We ordered lab
kit items in bulk and where possible directly from manufacturers to reduce the costs of the
items. Each General Physics Laboratory I kit costs \$20.60, and each
General Physics Laboratory II kit costs \$39.00. Table \ref{tab: 1251 lab kit} shows the lab
kit contents for General Physics Laboratory I, and Table \ref{tab: 1261 lab kit} shows the lab
kit contents for General Physics Laboratory II.
